Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
added method overview

\section{2D-3D Matching using Non-Zero Whitened Histograms of Orientations(NZ-WHO)}
\label{sec:nz-who}

\subsection{Overview}
Our method attempts to match CAD models

Our method is in line with \cite{Aubry14, Lim14} in the sense that we
use only renderings, not real images. However, rather than using fixed
sized mid-level patches, we use whole objects and make root
templates. By using root templates, there is no need to learn a
discriminative patch dictionary or to calibrate the patches and an
additional inference stage is not required. However, whitening the
whole template is prohibitive for several reasons. All templates have
different aspect ratios making it difficult to generate the covariance
matrix $\Sigma$. Since the root templates are larger than mid-level
patches, a very large auto-covariance $\Gamma$ is required. Lastly,
time complexity of decorrelating a template with $n$ cells increases
as $O(n^3)$, resulting in slow template generation and large residuals
due to numerical errors accumulated while decomposing the covariance
matrix $\Sigma$.

@@

>>>>

\section{Our Approach \scream{better name?}}
\label{sec:nz-who}

\subsection{Overview}
Our method attempts to match CAD models to 2D images, determining the best model within a class, its pose and scale, and the focal length of the camera used to produce the image. These parameters are first coarsely estimated using a discrete bank of detectors trained offline, before they are refined using MCMC by generating new detectors on the fly.

The basic detection method underlying our approach is HOG template matching. However, we propose a new HOG variant called Non-Zero Whitened Histograms of Orientations (NZ-WHO), where the HOG templates are whitened using statistics found from a random collection of natural images, producing a more discriminative template.

In addition to the library of CAD models that will be matched to the query images, our method requires a collection of random natural images. Offline, we compute HOG features of these images and record their mean and spatial autocovariance. The images are not used during testing, only the statistics generated from them.

Notably, we do not require any labelled training images of the objects to be detected. Our templates are generated exclusively by rendering CAD models from our library. From these renderings we produce novel HOG-like features we call Non-Zero Whitened Histograms of Orientations (NZ-WHO), which use the natural image statistics found offline to whiten a standard HOG template, making it more discriminative.

The matching proceeds in two steps: First, we apply a bank of pre-trained detectors to the image, corresponding to a set of discrete viewpoints, scales, and object models. This provides a rough estimate of these parameters. Second, we refine these parameters using MCMC, where each candidate is evaluated by rendering a new whitened template on the fly.

Optionally, our algorithm can be initialized using proposal bounding boxes from state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before executing the two steps above. In this scenario, our approach provides a means to augment standard bounding box detectors with more interesting 3D information.

\begin{comment}
Our method is in line with \cite{Aubry14, Lim14} in the sense that we
use only renderings, not real images. However, rather than using fixed
sized mid-level patches, we use whole objects and make root
templates. By using root templates, there is no need to learn a
discriminative patch dictionary or to calibrate the patches and an
additional inference stage is not required. However, whitening the
whole template is prohibitive for several reasons. All templates have
different aspect ratios making it difficult to generate the covariance
matrix $\Sigma$. Since the root templates are larger than mid-level
patches, a very large auto-covariance $\Gamma$ is required. Lastly,
time complexity of decorrelating a template with $n$ cells increases
as $O(n^3)$, resulting in slow template generation and large residuals
due to numerical errors accumulated while decomposing the covariance
matrix $\Sigma$.

@@

\end{comment}

\subsection{Non-Zero Whitened Histograms of Orientations (NZ-WHO)}
